\section*{}
Planning as heuristic search remains among the dominating approaches to many
variations of domain-independent planning, including classical planning,
temporal planning, planning under uncertainty and adversarial planning, for
nearly two decades. The research on both heuristics and search techniqes is
thriving, now more than ever, as evidenced by both the quality and the quantity
of submissions on the topic to major AI conferences and workshops.

This workshop seeks to understand the underlying principles of current
heuristics and search methods, their limitations, ways for overcoming those
limitations, as well as the synergy between heuristics and search. To this end,
this workshop intends to offer a discussion forum and a unique opportunity to
showcase new and emerging ideas to leading researchers in the area. Past
workshops have featured novel methods that have grown and formed indispensable
lines of research.

This year is the 11th edition of the workshop series on Heuristics for
Domain-independent Planning (HDIP), which was first held in 2007. HDIP
was subsequently held in 2009 and 2011. With the fourth workshop in
2012, the organizers sought to recognize the role of search algorithms
by acknowledging search in the name of the workshop, renaming it to
the workshop on Heuristics and Search for Domain-independent Planning
(HSDIP). The workshop continued flourishing under the new name and has
become an annual event at ICAPS.

\bigskip
\begin{flushright}
Guillem Franc\`es,
Florian Gei{\ss}er,
Daniel Gnad,
Patrik Haslum,\\
Florian Pommerening,
Miquel Ramirez,
Jendrik Seipp,
and Silvan Sievers
\\
July 2019
\end{flushright}
