\section*{}


Heuristic search is one of the main approaches in many
domain-independent planning variants, including classical planning,
temporal planning, planning under uncertainty and adversarial
planning.

The workshop on Heuristics and Search for Domain-Independent Planning
(HSDIP) is the eighth workshop in a series that started with the
”Heuristics for Domain-Independent Planning” (HDIP) workshops at ICAPS
2007, 2009 and 2011. At ICAPS 2012, the workshop was held for the
fourth time and was changed to its current name and scope to
explicitly encourage work on search for domain-independent planning.
It was very successful under both names. Many ideas presented at these
workshops have led to contributions at major conferences and pushed
the frontier of research on heuristic planning in several directions,
both theoretically and practically. The workshops, as well as work on
heuristic search that has been published since then, have also shown
that there are many exciting open research opportunities in this area.
Given the considerable success of the past workshops, and since it has
de facto become an annual event, we intend to continue holding it
annually.

The main focus of the HSDIP workshop series is on contributions that
help us find a better understanding of the ideas and principles
underlying current heuristics and search techniques, their
limitations, ways for overcoming those limitations, as well as the
synergy between heuristics and search. While the workshop series has
originated mainly in classical planning, it is very much open to new
ideas on heuristic schemes for more general settings, such as temporal
planning, planning under uncertainty and adversarial
planning. Contributions do not have to show that a new heuristic or
search algorithm ``beats the competition''. Above all we seek crisp
and meaningful ideas and understanding. Also, rather than merely being
interested in the ``largest'' problems that current heuristic search
planners can solve, we are equally interested in the simplest problems
that they cannot actually solve well.

We hope that the workshop will constitute one more step towards a
better understanding of the ideas underlying current heuristics and search
techniques, of their limitations, and of ways for overcoming those.

\bigskip
\noindent
We thank the authors for their submissions and for their hard work.

\vspace{0.5cm}
\begin{flushright}\noindent
  June 2016\hfill J. Benton, Daniel Bryce, Michael Katz, Nir Lipovetzky, Christian Muise, Miquel Ramirez, {\'A}lvaro Torralba.
\end{flushright}
